---
title: "GWR-Based Analysis of Influencing Factors on Car Ownership in Zhejiang Province, China"
author: "Zhiyuan Li"
date: "2021/1/11"
output: html_document
---
```{r, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, results = TRUE, message=FALSE, warning=FALSE)
```

## 1. Prepocess

```{r}
library(broom)
library(corrplot)
library(grid)
library(gridExtra)
library(htmlwidgets)
library(leaflet)
library(moments) 
library(psych)
library(plyr)
library(rgdal)
library(rgeos)
library(spdep)
library(sf)
library(sp)
library(spgwr)
library(tmap)
library(tmaptools)
library(tidyverse)
library(car)
# Change the presentation of decimal numbers to 4 and avoid scientific notation
options(prompt="R> ", digits=4, scipen=999)
```  

Download the data source we uploaded online earlier.

```{r}
download.file("https://github.com/lizhiyuan913/GIS-assessment/archive/main.zip", destfile="source.zip")
unzip("source.zip")
```  

Then read in the data, and have an overview.

```{r}
Automobile.data <- read.csv("./GIS-assessment-main/data.csv", sep=',')
glimpse(Automobile.data)
```

Chinese names of cities here are used for joining datas. 

```{r}
variable.name <- c("car.ownership", "population", "per.GDP", "household.price", "population.density", "urbanization", "milage.roadway", "ratio.bus", "prefectrue", "municipal.district")
names(Automobile.data)[3:12] <- variable.name
```  

Read in the map.

```{r}
Output.Areas <- readOGR("./GIS-assessment-main", "district", use_iconv = TRUE, encoding = "UTF-8")
```  

Name the columns.

```{r}
names(Output.Areas)[1:2] <- c("市级","县级")
```

Merge the two datasets.

```{r}
OA.Automobile <- merge(Output.Areas, Automobile.data, by.x="县级", by.y="市县名称", all=FALSE)
```

```{r}
head(OA.Automobile, 5)
```

```{r}
any(is.na(OA.Automobile@data)) #check missing value
```

Firstly, we calculate Moran's I for every varaible to see if it is geo-related.

```{r}
nb <- poly2nb(OA.Automobile)
lw <- nb2listw(nb, style="W", zero.policy=TRUE)
```

Some variables are very geographically related.

```{r}
for(i in names(OA.Automobile)[6:15]){
global.moran <- moran.test(OA.Automobile[[i]],lw, na.action = na.exclude, zero.policy=TRUE)
print(i)
print(global.moran$estimate[1])}
```

Lets have a look at the dependent variables.

```{r}
qtm(OA.Automobile, fill=variable.name[2:8], fill.palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), n=9, title=variable.name[2:8]) + tm_scale_bar(position=c("left", "bottom"))
```


Then we have a look at the distribution of the car ownership -- the independent variable.

```{r}
boxplot(Automobile.data[3], main="boxplot of car ownership")
qtm(OA.Automobile, fill="car.ownership", fill.palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), title="boxplot of car ownership") + tm_scale_bar(position=c("left", "bottom"))
```

We can see there are two strange  places.  
After checking the data, we notice that data for Jindong district is 0 and remove it.

```{r}
Automobile.data <- Automobile.data[-42,]
OA.Automobile <- merge(Output.Areas, Automobile.data, by.x="县级", by.y="市县名称", all=FALSE)
```

## 2. Regression
Set up the regression pattern. Perform a linear regression first.

```{r}
formula <- paste0("car.ownership ~", paste(names(Automobile.data)[4:12], collapse=' + '))
model <- lm(formula, data = OA.Automobile)
glance(model)
```

We can see the R2 is 0.4 and the p value is low.  
The residuals in my model is normally distributed from the above. So we can proceed on other validation.

```{r}
par(mfrow=c(2,2))
plot(model)
```

## 3. Skewness Test
Firstly, We draw see the distribution of variable.

```{r}
multi.hist(Automobile.data[4:10])
```

Then We run skewness test.

```{r}
skewness(Automobile.data[4:10])
```

We can see some variables turn out to be positively-skewed. So let's try symbox.
```{r}
for(i in c(4,6,7,9,10)){
symbox(Automobile.data[[i]])}
```

We choose to do the log transformation to skewed variables.
```{r}
for(i in c(4,6,7,9,10)){
Automobile.data[i] <- log10(Automobile.data[i])}
```

```{r}
skewness(Automobile.data[4:10])
```

Now all skewness is under control.

## 4. VIF Test

```{r}
par(mai=c(0,0,40,0), mex=2)
corrplot(cor(Automobile.data[4:10]), cl.pos="b", tl.col="black", main="Correlation matrix of the independent variables", mar=c(0,0,1,0), tl.cex=0.6)
```

We calculate the VIF to test multi-correlation.

```{r}
car::vif(model)
```

All the VIFs are under 5 thus do not need to remove.
Now try again.

```{r}
model <- lm(formula, data = OA.Automobile)
glance(model)
```

```{r}
par(mfrow=c(2,2))
plot(model)
```

## 5. Model Interpretation
Now let's see the variables' importance. We begin with the standardized coefficients of the variables.

```{r}
OA.Automobile.data.standardized <- lapply(OA.Automobile@data[, colnames(OA.Automobile@data)[6:15]], scale) 
model <- lm(formula, data = OA.Automobile.data.standardized)
model$coefficients
```

```{r}
par(mai=c(1,2,1,1))
barplot(model$coefficients, horiz=TRUE, las=1, main="Standardized coefficients of the variables")
```

We try to remove the variables one for a time and see how much the adjusted R2 drop.

```{r}
original <- summary(model)$adj.r.squared
for (i in 1:9){
formula.compare <- paste0("car.ownership ~", paste(names(Automobile.data)[4:12][-i], collapse=' + '))
model.compare <- lm(formula.compare, data=OA.Automobile)
print(names(Automobile.data)[4:12][i])
print(original - summary(model.compare)$adj.r.squared)}
```

It turns out that Road Milage，Household and Urbanization are the 3 most important variables. This is the same as above.

```{r}
resids <- residuals(model)
map.resids <- cbind(OA.Automobile, resids) 
names(map.resids)[length(names(map.resids))] <- "resids"
```

Draw residuals on the map.  

```{r}
qtm(map.resids, fill = "resids", text="city.name", scale=0.6, fill.palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), title="residuals") + tm_scale_bar(position=c("left", "bottom"))
```

We can see the residuals are very geo-related.So we decide to try GWR on it. 

## 6. Geographic Weighted Regression

```{r}
GWRbandwidth <- gwr.sel(formula, data = OA.Automobile, adapt = TRUE)
```

Train our GWR model.

```{r}
gwr.model = gwr(formula,
                data = OA.Automobile,
                adapt=GWRbandwidth,
                hatmatrix=TRUE,
                se.fit=TRUE)
gwr.model
```

After the GWR, the R2 is now up to 0.82, which is a huge imporvement from OLS.

```{r}
results <-as.data.frame(gwr.model$SDF)
```

```{r}
gwr.map <- cbind(OA.Automobile, as.matrix(results))
```

```{r}
variable.number.name <- paste(variable.name,".number", sep = "")
variable.coef.name <- paste(variable.name[-1],".coef", sep = "")
```

```{r}
names(gwr.map)[6:15] <- variable.number.name
names(gwr.map)[18:26] <- variable.coef.name
```

We draw the local R2 to have a better look.

```{r}
qtm(gwr.map, fill = "localR2",text="city.name", scale=0.6, fill.palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), title="localR2", format=) + tm_scale_bar(position=c("left", "bottom"))
```

We draw the parameters of every feature to have a better look.

```{r}
par(mfrow=c(3,4))
qtm(gwr.map, fill = variable.coef.name, scale=0.6, fill.palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), title=variable.coef.name) + tm_scale_bar(position=c("left", "bottom"))
```

## 7. Online Presentation
Draw the local R2, the 3 most impactable variables and their coefficients as different layers in one leaflet map.

```{r}
pick.variable.coef.name <- c("milage.roadway.coef", "urbanization.coef", "household.price.coef")
pick.variable.number.name <- c( "milage.roadway.number", "household.price.number", "urbanization.number")
```

```{r}
leaflet.tmap <- tm_shape(gwr.map) + tm_polygons(
c(pick.variable.coef.name, "localR2", pick.variable.number.name), palette=c("#ffffd9",
"#edf8b1",
"#c7e9b4",
"#7fcdbb",
"#41b6c4",
"#1d91c0",
"#225ea8",
"#253494",
"#081d58"), n=9) + tm_facets(as.layers = TRUE)
tmap_leaflet(leaflet.tmap)
```